### 2018-03-23 morus.tex
morus1280 version of trail

\begin{figure}
  \newcommand{\M}[2]{1.65,-1.5*#1-.25-.25*#2}
  \newcommand{\C}[1]{-.1,-.25-1.5*#1}
  \renewcommand{\S}[2]{.25+.25*#2,-1.5*#1}
  \centering
  \begin{subfigure}{\textwidth}
    \begin{tikzpicture}[xscale=3, yscale=1.5, every node/.style={font=\scriptsize,inner sep=2pt}]
      \begin{scope}
        \foreach \r in {0,...,3} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
        \foreach \r in {0,...,4} { \draw (\S{0}{\r}) node[above] {$S^{\r}$}; }
        \draw (\C{0}|-\S{0}{0}) node[above] {$C$};

@@

        \draw (\S{5}{2}) node[above] {\normalsize weight 9 (not 11)};
      \end{scope}
    \end{tikzpicture}
    \caption{\cipher{MiniMORUS-640}}
  \end{subfigure}
  \bigskip

  \begin{subfigure}{\textwidth}

    \caption{\cipher{MiniMORUS-1280}}
  \end{subfigure}
  \caption{\cipher{MiniMORUS}: Two approximations for $S^{2,2}_0$}
\end{figure}

>>>>

\begin{figure}
  \newcommand{\M}[2]{1.65,-1.5*#1-.25-.25*#2}
  \newcommand{\C}[1]{-.1,-.25-1.5*#1}
  \renewcommand{\S}[2]{.25+.25*#2,-1.5*#1}
  \centering
  \begin{tikzpicture}[xscale=3, yscale=1.5, every node/.style={font=\scriptsize,inner sep=2pt}]
    \begin{scope}
      \foreach \r in {0,...,3} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
      \foreach \r in {0,...,4} { \draw (\S{0}{\r}) node[above] {$S^{\r}$}; }
      \draw (\C{0}|-\S{0}{0}) node[above] {$C$};

@@

      \draw (\S{5}{2}) node[above] {\normalsize weight 9 (not 11)};
      \draw (\S{0}{2}) node[below] {\normalsize \cipher{MiniMORUS-640}};
    \end{scope}

    \draw[dashed] (\S{4.25}{-1}) -- (\S{4.25}{7}) -- ++(\S{1}{-1}) -- ++(\S{0}{7});

    \begin{scope}[yshift=-7.0cm]
      \foreach \r in {0,...,3} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
      \foreach \r in {0,...,4} { \draw (\S{0}{\r}) node[above] {$S^{\r}$}; }
      \draw (\C{0}|-\S{0}{0}) node[above] {$C$};

      \draw[alpha] (\C{0}) node[left] {51} -| (\S{1}{0}) node[above right] {0}
                   (\M{0}{0}) node[right] {$\alpha_{51}$};

      \draw[beta]  (\C{1}) node[above left] {0} -| (\S{1}{0}) node[below right] {0}
                   (\C{1}-|\S{1}{0}) -| ([xshift=-1pt]\S{1}{1}) node[above] {0\,}
                   (\M{1}{0}) node[right] {$\beta_0$};
      \draw[alpha] ([yshift=-1.5pt]\C{1}) node[left] {55} -| (\S{2}{0}) node[above right] {\!4}
                   (\M{1}{1}) node[right] {$\alpha_{55,33}$};
      \draw[alpha] ([yshift=-3.0pt]\C{1}) node[below left] {33} -| ([xshift=-1pt]\S{2}{0}) node[above left] {46\!};
      \draw[gamma] (\S{1}{1}) node[above] {\,0} -- (\S{2}{1}) node[above left] {46\!}
                   (\S{1}{1}) ++(0,-.75) -| ([xshift=-1pt]\S{1}{4}) node[above] {0\,}
                   (\M{1}{2}) node[right] {$\gamma_0$};
      \draw[delta] (\S{1}{4}) node[above] {\,0} -- (\S{2}{4}) node[above right] {4}
                   (\S{1}{4}) ++(0,-1.25) -| ([xshift=2pt]\S{2}{2}) node[below] {0} node[black] {$\times$}
                   (\M{1}{3}) node[right] {$\delta_0$};

      \draw[beta]  (\C{2}) node[above left] {46} -| ([xshift=-1pt]\S{2}{0}) node[below left] {46\!}
                   ([xshift=-1pt]\C{2}-|\S{2}{0}) -| (\S{2}{1}) node[below left] {46\!}
                   (\M{2}{0}) node[right] {$\beta_{4,46}$};
      \draw[beta]  ([yshift=-1.5pt]\C{2}) node[left] {4} -| (\S{2}{0}) node[below right] {\!4}
                   ([yshift=-1.5pt]\C{2}-|\S{2}{0}) -| ([xshift=1pt]\S{2}{1}) node[above] {\,\,\,4};
      \draw[alpha] ([yshift=-3.0pt]\C{2}) node[below left] {37} -| (\S{3}{0}) node[above right] {50}
                   (\M{2}{1}) node[right] {$\alpha_{37}$};
      \draw[gamma] ([xshift=2pt]\S{2}{1}) node[below right] {4} -- ([xshift=2pt]\S{3}{1}) node[above right] {50}
                   ([xshift=2pt]\S{2}{1}) ++(0,-.75) -| (\S{2}{4}) node[below right] {4}
                   (\M{2}{2}) node[right] {$\gamma_{4}$};

      \draw[beta]  (\C{3}) node[left] {50} -| (\S{3}{0}) node[below right] {50}
                   (\C{3}-|\S{3}{0}) -| ([xshift=2pt]\S{3}{1}) node[below right] {50}
                   (\M{3}{0}) node[right] {$\beta_{50}$};

      \draw (\S{4}{2}) node[above] {\normalsize weight 7 (not 9)};
      \draw (\S{5}{2}) node[above] {\normalsize \cipher{MiniMORUS-1280}};
    \end{scope}

    \begin{scope}[xshift=2.5cm,yshift=-7.0cm]
      \foreach \r in {1,...,4} { \draw[gray, rounded corners=2pt] (0,-\r*1.5) rectangle ++(1.5,-1.5); }
      \foreach \r in {0,...,4} { \draw (\S{1}{\r}) node[above] {$S^{\r}$}; }
      \draw (\C{0}|-\S{1}{0}) node[above] {$C$};

      \draw[alpha] (\C{1}) node[left] {25} -| (\S{2}{0}) node[above right] {38}
                   (\M{1}{0}) node[right] {$\alpha_{25}$};

      \draw[beta]  (\C{2}) node[above left] {38} -| (\S{2}{0}) node[below right] {38}
                   (\C{2}-|\S{2}{0}) -| ([xshift=-1pt]\S{2}{1}) node[above] {38\,}
                   (\M{2}{0}) node[right] {$\beta_{38}$};
      \draw[alpha] ([yshift=-1.5pt]\C{2}) node[left] {7} -| (\S{3}{0}) node[above right] {\!20}
                   (\M{2}{1}) node[right] {$\alpha_{7,1,51}$};
      \draw[alpha] ([yshift=-3.0pt]\C{2}) node[below left] {29} -| ([xshift=-1pt]\S{3}{0}) node[above left] {42\!};
      \draw[alpha] ([yshift=-4.5pt]\C{2}) node[below] {\,\,\,\,51} -| ([xshift=-4pt]\S{3}{0}) node[below] {0\,\,\,};
      \draw[gamma] (\S{2}{1}) node[above right] {38} -- (\S{3}{1}) node[above left] {20\!}
                   (\S{2}{1}) ++(0,-.75) -| ([xshift=-1pt]\S{2}{4}) node[above left] {38}
                   (\M{2}{2}) node[right] {$\gamma_{38}$};
      \draw[delta] (\S{2}{4}) node[above] {\,38} -- (\S{3}{4}) node[above right] {42}
                   (\S{2}{4}) ++(0,-1.25) -| ([xshift=1pt]\S{3}{2}) node[below right] {38}
                   (\M{2}{4}) node[right] {$\delta_{38}$};
      \draw[epsil] (\S{2}{2}) node[above] {0} node[black] {$\times$} -- (\S{3}{2}) node[below] {38}
                   (\S{2}{2}) ++(0,-1.00) -| ([xshift=-5pt]\S{3}{0}) node[above left] {0}
                   (\M{2}{3}) node[right] {$\varepsilon_0$};

      \draw[beta]  (\C{3}) node[above left] {42} -| ([xshift=-1pt]\S{3}{0}) node[below left] {42\!}
                   ([xshift=-1pt]\C{3}-|\S{3}{0}) -| (\S{3}{1}) node[below left] {42\!}
                   (\M{3}{0}) node[right] {$\beta_{20,42}$};
      \draw[beta]  ([yshift=-1.5pt]\C{3}) node[left] {20} -| (\S{3}{0}) node[below right] {\!20}
                   ([yshift=-1.5pt]\C{3}-|\S{3}{0}) -| ([xshift=1pt]\S{3}{1}) node[above] {\,\,\,\,20};
      \draw[alpha] ([yshift=-3.0pt]\C{3}) node[below left] {11} -| (\S{4}{0}) node[above right] {24}
                   (\M{3}{1}) node[right] {$\alpha_{11}$};
      \draw[gamma] ([xshift=2pt]\S{3}{1}) node[below right] {42} -- ([xshift=2pt]\S{4}{1}) node[above right] {24}
                   ([xshift=2pt]\S{3}{1}) ++(0,-.75) -| (\S{3}{4}) node[below right] {42}
                   (\M{3}{2}) node[right] {$\gamma_{42}$};

      \draw[beta]  (\C{4}) node[left] {24} -| (\S{4}{0}) node[below right] {24}
                   (\C{4}-|\S{4}{0}) -| ([xshift=2pt]\S{4}{1}) node[below right] {24}
                   (\M{4}{0}) node[right] {$\beta_{24}$};

      \draw (\S{5}{2}) node[above] {\normalsize weight 9 (not 11)};
    \end{scope}
  \end{tikzpicture}
  \caption{\cipher{MiniMORUS}: Two approximations for $S^{2,2}_0$}
\end{figure}
